---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickanalysis

<!-- badges: start -->
<!-- badges: end -->

The goal of quickanalysis is quickly analyze any measured numeric variable 
across multiple treatments, and want a quick summary statistics and
visualization of the data. The `box_and_stats()` function provides fast 
summary statistics (min, max, mean, median, standard deviation) of the measured 
variable for each treatment, along with a boxplot which displays the data 
visually.

## Installation

quickanalysis is not on CRAN, but you can download it from my github repository. 
Use the follwoing R command to download it:

``` r
 devtools::install_github("marquenis/quickanalysis") 
```

## Example

This is a basic example of how the package works using the built in R dataset: 
iris. This dataset contains a measured variable (Sepal.length) across multiple categorical treatments (in this case, species). 

By running this function we can see the maximum, minimum, mean, median, and 
standard deviation of the sepal length of the flowers, grouped by their 
different species. 

It also creates a boxplot that lets us visually see the distribution of sepal 
length grouped by species. From this quick boxplot we can see that different 
species have different sepal lengths, and conduct further statistical analyses. 

```{r example}
library(quickanalysis)

box_and_stats(iris, Species, Sepal.Length)
```

This package is special because all those analysis can be completed just
by loading the package and running a single line of code. 

## Notes

Please be aware that this package relies on the following 3 packages for 
internal coding use:
1. dplyr
2. ggplot2
3. magittr

