---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickanalysis

<!-- badges: start -->
<!-- badges: end -->

The goal of quickanalysis is quickly analyze any measured numeric variable 
across multiple treatments, and want a quick summary statistics and
visualization of the data. The `box_and_stats()` function provides fast 
summary statistics (min, max, mean, median, standard deviation) of the measured 
variable for each treatment, along with a boxplot which displays the data 
visually.

## Installation

quickanalysis is not on CRAN, but you can download it from my github repository. 
Use the follwoing R command to download it:

``` r
 devtools::install_github("marquenis/quickanalysis") 
```

## Example

This is a basic example of how the package works using the R dataset iris. This
dataset contains a measured variable (Sepal.length) across multiple categorical 
treatments (in this case, species). 

```{r example}
library(quickanalysis)

box_and_stats(iris, Species, Sepal.Length)
```

This package is special because you can easily do all that jazz

## Notes

One interesting thing about this package is it relies on ggplot2, dplyr, and magrittr


